\chapter{Glossary}
\textbf{CRUD}        \textbf{C}reate, \textbf{R}ead, \textbf{U}pdate and, \textbf{D}elete – A collection of resource functions to manage RESTful resources for managing resources. They roughly correspond to the SQL actions of Insert, Select, Update, and Delete, respectively.

\textbf{Datacenter}      A physical location housing the primary servers and network infrastructure.

\textbf{Fleet}      a group of sites belonging to a single entity (e.g. all of the vessels owned  by Acme Corp)

\textbf{NEMA}        

\textbf{Node}– A device on the remote that collects the event data and creates messages. The node is responsible for holding the messages until such time as they can be transmitted to the server.

\textbf{Out-of-band}– The transfer of information outside of the common communication channel or network.

\textbf{GUI}– Graphical User Interface

\textbf{In-flight}- Information that is in the state of being transferred.

\textbf{JSON}– Javascript Object Notation

\textbf{REST}– \textbf{RE}presentative \textbf{S}tate \textbf{T}ransition – This is the protocol that provides the web services used between the node and the server.{Fielding:2000dd}

\textbf{ROV} – \textbf{R}emotely \textbf{O}perated \textbf{V}ehicle. A remotely operated submarine for the context of this paper.{Christ:2011vn}

\textbf{SNMP} – Simple Network Management Protocol

\textbf{SSD} – Solid State Disk

\textbf{Tendril} – A connection which provides event data to a node. May be physical or virtual.

\textbf{Shorebase} – A physical location housing the server equipment. This is often an office or a datacenter.

\textbf{UPnP} – Universal Plug and Play

\textbf{VSAT}	-Very Small Apeture Terminal. These are the terminals used in Satellite communications. Typically smaller than 1m2 and used on the remote end of an satellite link.
